\chapter{OBSERVATIONS AND DISCUSSIONS}\label{ch:experimental_result}
\subsection{Process Efficiency}
The Kanban system proved highly effective for visualizing workflow. The movement of sticky notes provided immediate status updates to all team members. Parallel execution of independent tasks reduced overall completion time by approximately 40\% compared to sequential execution. The testing column created a natural quality check, catching calculation errors before finalization.

\subsection{Team Dynamics}
\begin{itemize}
    \item \textbf{Role Specialization:} Lineya naturally assumed calculation tasks, while Rohan handled data collection. Shihab managed ambiguous tasks, and Marufa focused on survey-based activities.
    \item \textbf{Communication Patterns:} Initial confusion in task interpretation (particularly "Climb Mount Everest") highlighted the need for clearer task definitions.
    \item \textbf{Verification Culture:} The peer testing requirement fostered accountability, though some resistance was noted when team members had to wait for verification.
\end{itemize}

\subsection{Challenges Encountered}
\begin{enumerate}
    \item \textbf{Data Inconsistency:} The "units studied" task produced conflicting results (Table \ref{tab:results}), indicating either unclear instructions or recording errors.
    \item \textbf{Task Ambiguity:} The metaphorical "Climb Mount Everest" task required team interpretation, leading to varied approaches.
    \item \textbf{Name Variations:} Spelling inconsistencies (Shihab, Rohan) appeared across documentation.
    \item \textbf{Resource Constraints:} Limited writing space on sticky notes forced abbreviated responses.
\end{enumerate}

\subsection{Lessons Learned}
\begin{itemize}
    \item \textbf{Visual Management:} Physical movement of tasks creates shared understanding and ownership.
    \item \textbf{Parallel Execution:} Independent tasks should be identified early for efficiency.
    \item \textbf{Quality Assurance:} Peer verification reduces errors but requires clear protocols.
    \item \textbf{Documentation:} Photographic evidence provides valuable process insights.
    \item \textbf{Flexibility:} Teams must adapt to ambiguous tasks with creative solutions.
\end{itemize}

\subsection{Process Improvements}
Based on observations, the following improvements are recommended:
\begin{enumerate}
    \item Implement a task clarification phase before execution
    \item Use standardized templates for data collection tasks
    \item Assign explicit verifiers for each testable task
    \item Include a "Blocked" column for tasks awaiting dependencies
    \item Conduct brief stand-up meetings between state transitions
\end{enumerate}