\chapter{Functional Requirements and User Stories} \label{ch:functional}

The following chapter outlines the core functional requirements, user stories, and feature assignments for the Multi-Tenant E-Commerce System. Each requirement is linked to a responsible team member for implementation.

\section{Functional Modules and Responsibilities}

\begin{enumerate}
    \item \textbf{Sign-Up and Security Management (Shihab)}
    \begin{itemize}
        \item \textbf{Features:} 
        \begin{itemize}
            \item Two-Factor Authentication (2FA) during registration and login.
            \item Vendor certificate verification and Tax Identification Number (TIN) validation.
            \item Shop deletion or deactivation functionality.
            \item Secure storage of sensitive information in the database.
        \end{itemize}
        \item \textbf{User Stories:}
        \begin{itemize}
            \item As a vendor, I want to securely register with 2FA so that my account is protected.
            \item As a Super Admin, I want to verify vendor certificates and TINs to ensure only legitimate businesses are onboarded.
            \item As a vendor, I want the option to delete my shop if I stop operations, ensuring control over my data.
        \end{itemize}
    \end{itemize}

    \item \textbf{Offer and Theme Customization (Rohan)}
    \begin{itemize}
        \item \textbf{Features:}
        \begin{itemize}
            \item Creation and management of promotional offers and discounts.
            \item Customization of storefront themes, including colors, logos, and banners.
        \end{itemize}
        \item \textbf{User Stories:}
        \begin{itemize}
            \item As a vendor, I want to design my store with custom themes to maintain brand identity.
            \item As a vendor, I want to run time-limited offers so that I can attract more customers.
        \end{itemize}
    \end{itemize}

    \item \textbf{Payment Gateway Integration and Product Tracking (Lineya)}
    \begin{itemize}
        \item \textbf{Features:}
        \begin{itemize}
            \item Integration with predefined payment gateways: bKash, Nagad, Cash on Delivery (COD), Visa, MasterCard.
            \item Tracking product orders, including status updates from processing to delivery.
        \end{itemize}
        \item \textbf{User Stories:}
        \begin{itemize}
            \item As a customer, I want multiple secure payment options so that I can pay conveniently.
            \item As a vendor, I want to track the status of each order to manage deliveries efficiently.
        \end{itemize}
    \end{itemize}

    \item \textbf{Inventory Management and Analytical Dashboard (Marufa)}
    \begin{itemize}
        \item \textbf{Features:}
        \begin{itemize}
            \item Maintain and update product inventory in real-time.
            \item Analytical dashboard to monitor sales, revenue, and inventory trends.
        \end{itemize}
        \item \textbf{User Stories:}
        \begin{itemize}
            \item As a vendor, I want my inventory automatically updated with each order to prevent overselling.
            \item As a vendor, I want a dashboard displaying sales trends to make informed business decisions.
        \end{itemize}
    \end{itemize}

    \item \textbf{Promotional Notifications and Feedback Management (Taskif)}
    \begin{itemize}
        \item \textbf{Features:}
        \begin{itemize}
            \item Sending promotional notifications to customers for offers or product updates.
            \item Collecting and managing customer feedback, including ratings and reviews.
        \end{itemize}
        \item \textbf{User Stories:}
        \begin{itemize}
            \item As a vendor, I want to send notifications to my customers to increase engagement and sales.
            \item As a vendor, I want to view and respond to customer reviews to improve service quality.
        \end{itemize}
    \end{itemize}
\end{enumerate}

This chapter establishes the core functional areas of the Multi-Tenant E-Commerce System, aligning each requirement with specific user stories and responsible team members. This structured assignment ensures clarity in development, accountability, and comprehensive coverage of the system’s functional expectations.

\clearpage
