\chapter{OBJECTIVE}\label{obj}
This laboratory experiment focuses on exploring and evaluating different UML (Unified Modeling Language) drawing tools through collaborative teamwork. The activity introduces students to various diagramming tools used in Object-Oriented Analysis and Design (OOAD) and helps them understand how to select appropriate tools for project development. By researching, comparing, and presenting multiple UML tools, students gain practical exposure to teamwork, task distribution, and tool selection, which are essential in software development environments.

\section{Objectives}

The objectives of this laboratory activity are as follows:

\begin{itemize}
  \item To form a project team and assign different UML tools to each member.
  \item To develop teamwork, research, and communication skills among team members.
  \item To explore the features and functionalities of commonly used UML drawing tools.
  \item To identify the advantages and limitations of each UML tool.
  \item To compare different tools based on usability, cost, collaboration, and platform support.
  \item To select the most suitable UML tool for team project work.
  \item To document findings and prepare a structured team report.
  \item To gain practical understanding of UML tools used in Object-Oriented Analysis and Design (OOAD).
\end{itemize}

\section{Expected Outcomes}

At the end of this laboratory activity, the following outcomes are expected:

\begin{itemize}
  \item Successful formation of a project team with task distribution among members.
  \item Completion of individual research on assigned UML tools.
  \item Compilation of a comparative report on five UML drawing tools.
  \item Identification of advantages and limitations of each tool.
  \item Selection and justification of the most suitable UML tool for the team project.
  \item Improved understanding of UML diagram creation and tool usage.
  \item Enhanced teamwork, collaboration, and report-writing skills.
  \item Preparation for future software design and OOAD laboratory activities.
\end{itemize}
