\chapter{OBSERVATIONS AND DISCUSSIONS}
\label{ch:observations}

This chapter discusses the observations made during the laboratory activity and analyzes the effectiveness of using collaborative tools and UML diagram software for completing the team-based assignment.

\begin{itemize}
  \item Assigning different UML tools to each team member allowed the team to explore a wide range of diagramming platforms and understand their unique features.
  
  \item The use of Trello provided a clear visual workflow with \textit{To Do}, \textit{Doing}, and \textit{Done} columns, which helped track progress and manage tasks efficiently.
  
  \item Discord communication enabled quick discussion, task clarification, and file sharing among team members, improving coordination and teamwork.
  
  \item Independent research on assigned tools helped develop individual understanding while still contributing to the team report.
  
  \item Creating sample UML diagrams in each tool allowed members to compare usability, features, and flexibility in real scenarios.
  
  \item Screenshot evidence from Trello and Discord served as proof of participation, task completion, and collaboration.
  
  \item During the comparison phase, Draw.io was observed to be the most suitable tool due to its free access, simple interface, wide template support, and easy export options.
  
  \item The activity demonstrated how collaborative platforms and diagramming tools can be integrated effectively in software engineering workflows.
  
  \item Instructor feedback highlighted the importance of documentation, tool comparison, and proper communication in team-based software projects.
\end{itemize}
